\documentclass[sigconf, authorversion]{acmart}
\settopmatter{authorsperrow=4} % not sure if this is allowed but this looks much better

\usepackage{enumitem}
\usepackage{graphicx}  % another package that works for figures
\usepackage{booktabs} % For formal tables
\usepackage{cleveref} % for better references
\usepackage{caption,subcaption}
% \usepackage[english]{babel}% already included
\usepackage{csquotes}% Recommended
\usepackage{siunitx}
\usepackage{tabularx,acmart-taps}
\usepackage{xcolor}
\usepackage{rotating}
\usepackage{lscape}
\usepackage{afterpage}
\usepackage{hyperref}
\hypersetup{breaklinks=true}
\usepackage{wrapfig}
\usepackage{float}
% \usepackage{sidecap}
% \usepackage{adjustbox} 

\usepackage{framed} % replacing \usepackage{mdframed}
\usepackage{fontawesome} % for the icon
% \usepackage{tcolorbox}

\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

% Bibliography
\bibliographystyle{ACM-Reference-Format}
\usepackage{url}
% \setcounter{biburllcpenalty}{7000}
% \setcounter{biburlucpenalty}{8000}

% macros
% \newtcolorbox{tldrbox}[1][]{colback=gray!10, colframe=darkgray, left=5pt, right=5pt, top=3pt, bottom=3pt, arc=0pt, outer arc=0pt, toprule=0pt, bottomrule=0pt, leftrule=1.5pt, rightrule=0pt, #1}
\definecolor{lightgray}{gray}{0.9}
\definecolor{darkgray}{gray}{0.4}
\definecolor{darkred}{rgb}{0.6, 0, 0}

% quote macros
\input{content/macros/quotes}

%% author color
%% color: http://latexcolor.com/
\definecolor{lapislazuli}{rgb}{0.15, 0.38, 0.61}
\newcommand{\hs}[1]{{\color{red}{HS: #1}}}
\newcommand{\tc}[1]{{\color{green}{TC: #1}}}
\newcommand{\lwt}[1]{{\color{olive}{LWT: #1}}}
\newcommand{\kk}[1]{{\color{violet}{KK: #1}}}
\newcommand{\vk}[1]{{\color{blue}{VK: #1}}}
\newcommand{\yhc}[1]{{\color{orange}{YHC: #1}}}
\newcommand{\change}[1]{{\color{black}{#1}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\copyrightyear{2025}
\acmYear{2025}
\setcopyright{cc}
\setcctype{by-nc}
\acmConference[CHI '25]{CHI Conference on Human Factors in Computing Systems}{April 26-May 1, 2025}{Yokohama, Japan}
\acmBooktitle{CHI Conference on Human Factors in Computing Systems (CHI '25), April 26-May 1, 2025, Yokohama, Japan}\acmDOI{10.1145/3706598.3714193}
\acmISBN{979-8-4007-1394-1/25/04}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\AtBeginMaketitle{%
\let\oldAtBeginDocument\AtBeginDocument%
\renewcommand\AtBeginDocument[1]{#1}
\setcopyright{cc}
\setcctype{by-nc}
\copyrightyear{2025}
\acmYear{2025}
\acmDOI{10.1145/3706598.3714193}
\acmISBN{979-8-4007-1394-1/25/04}
\acmConference[CHI '25]{CHI Conference on Human Factors in Computing Systems}{April 26--May 01, 2025}{Yokohama, Japan}
\acmBooktitle{CHI Conference on Human Factors in Computing Systems (CHI '25), April 26--May 01, 2025, Yokohama, Japan}
\let\AtBeginDocument\oldAtBeginDocument%
}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
% \title[QV vs Likert]{``\textellipsis I can show what I really like.'': 
% Comparing Quadratic Voting with Likert Surveys at aligning respondents' preferences}

\title{Organize, Then Vote: Exploring Cognitive Load in Quadratic Survey Interfaces}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.


%% Author list
\input{metadata/authors/tcheng.tex}
\input{metadata/authors/yutong.tex}
\input{metadata/authors/hank.tex}
\input{metadata/authors/vkoshy.tex}
\input{metadata/authors/wenting.tex}
\input{metadata/authors/kkarahal.tex}
\input{metadata/authors/hs1.tex}

% %%
% %% By default, the full list of authors will be used in the page
% %% headers. Often, this list is too long, and will overlap
% %% other information printed in the page headers. This command allows
% %% the author to define a more concise list
% %% of authors' names for this purpose.
\renewcommand{\shortauthors}{Ti-Chung Cheng et al.}

\begin{abstract}
    Quadratic Surveys (QSs) elicit more accurate preferences than traditional methods like Likert-scale surveys. However, the cognitive load associated with QSs has hindered their adoption in digital surveys for collective decision-making. We introduce a two-phase ``organize-then-vote'' QS to reduce cognitive load. As interface design significantly impacts survey results and accuracy, our design scaffolds survey takers' decision-making while managing the cognitive load imposed by QS. In a 2x2 between-subject in-lab study on public resource allotment, we compared our interface with a traditional text interface across a QS with 6 (short) and 24 (long) options. Two-phase interface participants spent more time per option and exhibited shorter voting edit distances. We qualitatively observed shifts in cognitive effort from mechanical operations to constructing more comprehensive preferences. We conclude that this interface promoted deeper engagement, potentially reducing satisficing behaviors caused by cognitive overload in longer QSs. This research clarifies how human-centered design improves preference elicitation tools for collective decision-making.
\end{abstract}

\input{metadata/keywords.tex}

%% Main Text
\maketitle
\input{content/0_Introduction.tex}
\input{content/1_related_works.tex}
\input{content/2.1_interface_design.tex}
\input{content/2.2_experiment.tex}

\input{content/3.1_result_cognitive_load.tex}
\input{content/3.2_result_distance.tex}
\input{content/3.3_result_time.tex}

\input{content/4_discussion.tex}

\input{content/5_conclusion.tex}
\input{content/98_acks.tex}


% \printbibliography
\bibliography{tcheng}

% TC:ignore
\input{content/99_appendix}
% TC:endignore

\end{document}
\endinput

